---
title: "MLR_Class Assignment"
author: "Stephanie N. Pham"
date: "`r Sys.Date()`"
output: html_document
---
```{r comments, include=FALSE}
# rm(list= ls())
# install.packages("gridExtra")
# Script Name:
#   3_MLR.R
##
# Purpose: 
#   In this script, we will walk through the lm() procedure for MLR
#   including fitting the model and confidence/prediction intervals.
```

#   Bring in Athletes.csv dataset
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(gridExtra)

#######################################################

# Bring in the "athletes" data
setwd("C:/Users/phams/Virginia Tech/SP Sandbox - Documents/Coursework/Regression/3_MLR")
data <- read.csv(file = "2_athletes_data.csv")

```


#   Question 1
Plot the scatterplot and upload
```{r 1}
#My plot
plot(data$treadmill,data$km.run, 
     main="Scatterplot of Athletes Treadmill vs. 10 km Run Time", 
     xlab="Treadmill Time to Exhaustion", 
     ylab="10 km Run Time", 
     col="white", 
     bg="navy",
     cex=1.25, 
     pch=24)
```

#   Question 2
Fit and obtain the estimated linear regression model. What is the estimated slope?
```{r 2}
# Fit model and obtain linear regression model
mlr=lm(km.run~.,data=data)
lm_sum = summary(mlr)
lm_sum

# Answer: -1.8673 

```
#   Question 3
What is the estimated intercept?
```{r 3}
# Answer: 58.8158

```

#   Question 4
What is your estimate of sigma^2?
```{r 4}
# Answer: 4.417186
lm_sum$sigma^2

```
#   Question 5
What is your estimate of the standard error of B1(hat)?
```{r 5}
# Answer: 0.3462

```

#   Question 6 
What are the hypotheses for a test on whether there is a linear relationship 
between the amount of time needed to run a 10-km race and the time to exhaustion 
a treadmill?

H0: The amount of time needed to run a 10-km race is not affected by an athlete's time to exhaustion on a treadmill
Ha: The amount of time needed to run a 10-km race is affected by an athlete's time to exhaustion on a treadmill

#   Question 7
What is the test statistic for the hypothesis test described in Question 6?
```{r 7}
lm_sum$coefficients

# Answer: -5.393403
```

#   Question 8
What is your conclusion for the hypothesis test described in Question 6?

We can reject the null hypothesis, meaning that the amount of time needed to run a 10-km race is affected by an athlete's time to exhaustion on a treadmill. 
We can conclude this since the p-value (p = 3.99e-05) is smaller than the a=0.05, indicating that the chance that we can accept the null hypothesis is 
less than 5% of the time. 

