---
title: "hw1_regression"
author: "Stephanie N. Pham"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(gridExtra)
library(Rfit)
library(MASS)
#######################################################

# Bring in the "tvmarketing.csv" data
salary <- read.csv(file = "data/salary.csv")
```

Problem 1: A researcher in a scientific foundation wished to evaluate the relation between intermediate and
senior level annual salaries of bachelor’s and master’s level mathematicians (y, in thousand dollars) and an
index of work quality (xQuality), number of years of experience (xExperience), and an index of publication success
(xPublication). A portion of the data for a sample of 24 mathematicians is shown below (all data on Canvas).

```{r 1}

salary_fit = lm(Salary~., data=salary)


```


```{r 13}

confint(salary_fit,level=0.95)
```


```{r 15}
late_math = data.frame(Quality=5.4, Experience=17, Publication=6.0)
late_math$Salary = predict(salary_fit, newdata = late_math)

```

```{r 16}
all_math = rbind(salary, late_math)
all_math_fit = lm(Salary~., data = all_math)
all_math_fit_new = lm(Salary~1, data = all_math)
confint(all_math_fit_new, level=0.95)

predict(salary_fit,newdata=late_math, interval='confidence',level=0.95) # Confidence Intervals


```

```{r 17}

pred_intervals <- predict(all_math_fit, interval = "prediction", level = 0.95)
pred_intervals

```

```{r 18}

x = seq(0.5, 10, .5)
x = matrix(x, nrow=length(x), ncol=1)
beta_matrix = matrix(rep(0),nrow=500, ncol=2)
y_expect = matrix(rep(0),nrow=500, ncol=1)

for (k in 1:500){
  e = rnorm(length(x), 0, 16)
  y = 50+10*x+e
  y = matrix(y)
  mod_lm = lm(y~x)
  beta_matrix[k,] = t(matrix(c(mod_lm$coefficients[1],mod_lm$coefficients[2])))
  y_expect[k,] = mod_lm$coefficients[1] + mod_lm$coefficients[2]*5
}

intercepts = hist(beta_matrix[,1],main=NULL, xlab="beta 0")
slopes = hist(beta_matrix[,2],main=NULL, xlab="beta 1")
estimate = hist(y_expect, main=NULL, xlab="estimates")

#Q-Q Plot
qqnorm(stud,pch = 16);abline(0,1, col="red")
```

```{r 21}
# Bring in the "wine" data
wine <- read.csv(file = "data/problem_3.csv")
wine_fit = lm(Quality.Rating..y.~., data=wine)

# Scatterplot 
plot(wine$Sulfur.Content..x.,wine$Quality.Rating..y., 
     main="Sulfur Content x Quality Rating", 
     xlab="Sulfur Content", 
     ylab="Quality Rating", 
     col="navy", 
     bg="navy",
     cex=1.25, 
     pch=19)

# Studentized residuals
stud = rstudent(wine_fit)
wine_mod = fitted(wine_fit)


plot(wine_mod, stud,
     main="Studentized Residuals vs. Predicted", 
     xlab="Sulfur Content", 
     ylab="Studentized Residuals",
     ylim=(c(-4, 4))
     );

# Q-Q Plot
qqnorm(stud,pch = 16);abline(0,1, col="red")

# Shapiro-Wilk Test
shapiro.test(stud)

plot(1:length(stud), stud,
     main="Order vs. Studentized Residuals", 
     xlab="Order", 
     ylab="Studentized Residuals",
     ylim=(c(-4, 4)))

```
